\chapter{Conclusion}
In this chapter, we will have a summary of the progress for the first phase, and then discuss some plans for the next phase of the project.

\section{Summary}
In this first phase of the thesis, the goal is to learn and prepare the knowledge that is needed for the implementation of the project, specify the problem and the scope of the project as well as design the system architecture. To be more specific, we have done building the system architecture, learning the background knowledge, doing some research on the related works and developing the data crawler service and the intent classifier.

\subsection{Challenges}
Throughout the process of doing this project, we have faced some challenges:

\begin{itemize}
    \item The first thing and also the biggest challenge is the process of learning background knowledge. Both of us do not have much experience working in the field of Machine Learning and Natural Language Processing. But it is also an opportunity for us to learn new things. 

    \item The next challenge is in the process of crawling data from the internet. Some website has a lot of security measures to prevent the crawler from crawling the data. Therefore, we have to find a way to bypass these security measures.

    \item The last challenge is in the data processing. We have a lot of data, but to use the data for training the NER model, we have to annotate the data first. The process of annotating data is very time-consuming and requires a lot of effort.
\end{itemize}

\subsection{Experience}
\begin{itemize}
    \item Research and paper reading skill
    \item Time management for a big project
    \item Communication, task assignment between members
    \item Self-motivate and self-discipline
    \item NLP project experience
    \item Data crawling project experience
\end{itemize}

\section{Future Plan}
Regarding the plan for the next phase, there are still many main tasks that must be completed:

\begin{itemize}
    \item Prepare the dataset for training the NER model.
    \item Finish creating a Machine Reading Comprehension dataset and an Intent/Entity dataset.
    \item Implement the user interface for the website and chatbot.
    \item Implement the database and the back-end server.
    \item Testing and Evaluation
\end{itemize}